---
title: Exploration of pairwise distances (within)
subtitle:
author: Molly Lewis
date: "`r Sys.Date()`"
output:
  html_document:
    toc_float: no
    code_folding: hide
    number_sections: no
    toc: yes
---

```{r setup, include = F}
# load packages
library(knitr)
library(rmarkdown)
library(tidyverse)
library(here)
library(corrr)
library(langcog)

opts_chunk$set(echo = T, message = F, warning = F,
               error = F, tidy = F, cache = F)

```

```{r}

MEAN_COUNTRY_DISTS <- here("data/processed/mean_sim_by_country_item.csv")

mean_country_dists <- read_csv(MEAN_COUNTRY_DISTS,
                               col_names = c("category","country", "log_avg_haus_mean","log_avg_haus_sd" ,"mahalanobis_mean", "mahalanobis_sd", "euclidean_mean"  , "euclidean_sd", "human_predic_sim_mean","human_predic_sim_sd", "log_human_predic_sim_mean", "log_human_predic_sim_sd" ))
```

## Items
```{r}
by_category <- mean_country_dists %>%
  group_by(category) %>%
  mutate(log_human_predic_sim_sd = log(human_predic_sim_sd)) %>%
  select(category, human_predic_sim_mean, human_predic_sim_sd, log_human_predic_sim_sd) %>%
  summarize_if(is.numeric, mean, na.rm = T)  %>%
  rename(item = category)

```

```{r}
WITHIN_ITEM_PREDICTORS <- here("data/raw/predictors/within_item_predictors.csv")

item_predics <- read_csv(WITHIN_ITEM_PREDICTORS) 

all_measures <- by_category %>%
  left_join(item_predics) 

all_measures %>%
  select(item, category, everything()) %>%
  pivot_longer(3:7) %>%
  ggplot(aes(x = value)) +
  geom_histogram() +
  facet_wrap(~name, scale = "free")

all_measures_trans <- all_measures %>%
  mutate(log_aoa = log(aoa),
         log_auditory = log(auditory + .01),
         log_gustatory = log(gustatory + .01),
         log_olfactory = log(olfactory + .01),
         log_interoceptive = log(interoceptive + .01),
         sq_conc_m = conc_m^2) %>%
  select(-aoa, -auditory, -gustatory, -olfactory, -interoceptive) %>%
  select(item, category, human_predic_sim_mean, human_predic_sim_sd, log_human_predic_sim_sd, conc_m, sq_conc_m, log_aoa, arousal, log_freq, valence, dominance)

all_measures_trans %>%
  select(item, category, everything()) %>%
  pivot_longer(3:9) %>%
  ggplot(aes(x = value)) +
  geom_histogram() +
  facet_wrap(~name, scale = "free")
```

```{r}

var_pairs <- cross_df(list(var1 = names(all_measures_trans),
              var2 = names(all_measures_trans))) %>%
  filter(!(var1 %in% c("item", "category")),
         !(var2 %in% c("item", "category")))

get_cor <- function(v1, v2, d){
  cor.test(d[[v1]], d[[v2]]) %>% 
      tidy() %>%
    mutate(var1 = v1,
           var2 = v2) %>%
    select(var1, var2, everything())
} 

m = map2_df(var_pairs$var1, var_pairs$var2, get_cor, all_measures_trans)

corrs <- m %>%
  filter(var1 %in% c("human_predic_sim_mean", "human_predic_sim_sd", "log_human_predic_sim_sd"),
         !var2 %in% c("human_predic_sim_mean", "human_predic_sim_sd", "log_human_predic_sim_sd")) %>%
  arrange(p.value) %>%
  data.frame()

ggplot(corrs, aes(x = var2, y = estimate, color = var2)) +
  geom_pointrange(aes(ymin = conf.low, ymax = conf.high)) +
  facet_wrap(.~var1) +
  geom_hline(aes(yintercept = 0), linetype = 2) + 
  theme_classic() +
    theme(axis.text.x = element_text(angle = 90)) 


lm(human_predic_sim_sd ~ conc_m + log_aoa + arousal + log_freq + valence + dominance,  all_measures_trans) %>% 
  summary()

lm(human_predic_sim_mean ~ conc_m + log_aoa + arousal + log_freq + valence + dominance,  all_measures_trans) %>% 
  summary()

lm(log_human_predic_sim_sd ~ conc_m + log_aoa + arousal + log_freq + valence + dominance,  all_measures_trans) %>% 
  summary()
```

Words that are more frequent and more positively valences have more within country similarity, on average.
Words that are low arousal, low concreteness, high haptic, high aoa, low auditory, low frequency, low olfactory low valence have high variance. 

Words that are more frequent and more positively valences have more within country similarity, on average.
Words that are learned early, highly frequency,  high arousal and high valence, high concreteness have low variance. 

### By category
```{r}
all_measures_trans_by_cat_mean <- all_measures_trans %>%
  group_by(category) %>%
  multi_boot_standard(col = "human_predic_sim_mean")

ggplot(all_measures_trans_by_cat_mean, aes(x = fct_reorder(category, mean), y = mean, fill = category)) +
  geom_bar(stat = "identity") +
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper)) +
  geom_hline(aes(yintercept = 0), linetype = 2) + 
  theme_classic() +
  ylab("MEAN") +
    theme(axis.text.x = element_text(angle = 90),
                    legend.position = "none") 

all_measures_trans_by_cat_sd <- all_measures_trans %>%
  group_by(category) %>%
  multi_boot_standard(col = "human_predic_sim_sd")

ggplot(all_measures_trans_by_cat_sd, aes(x = fct_reorder(category, mean), y = mean, fill = category)) +
  geom_bar(stat = "identity") +
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper)) +
  geom_hline(aes(yintercept = 0), linetype = 2) + 
  theme_classic() +
  ylab("SD") +
    theme(axis.text.x = element_text(angle = 90), 
          legend.position = "none") 
```

## Countries

```{r}
COUNTRY_PREDIC_PATH <- here("data/raw/predictors/conceptqd\ predictors\ -\ within\ culture.csv")
country_predics <-  read_csv(COUNTRY_PREDIC_PATH) %>%
  clean_names() %>%
  select(country, country_name, pdi, uai, idv, mas, area, population_density, racial_diversity_ethnic, population, gini_index)

by_country <- mean_country_dists %>%
  group_by(country) %>%
  select(country, human_predic_sim_mean, human_predic_sim_sd) %>%
  summarize_if(is.numeric, mean, na.rm = T) 

country_with_predics <- by_country %>%
  left_join(country_predics)

country_with_predics %>%
  select(country, country_name, everything()) %>%
  pivot_longer(3:13) %>%
  ggplot(aes(x = value)) +
  geom_histogram() +
  facet_wrap(~name, scale = "free")

country_with_predics_tidy <- by_country %>%
  left_join(country_predics) %>%
  mutate(log_area = log(area),
         log_pop = log(population),
         log_pdi = log(pdi))

```

```{r}

var_pairs <- cross_df(list(var1 = names(country_with_predics_tidy),
              var2 = names(country_with_predics_tidy))) %>%
  filter(!(var1 %in% c("country", "country_name")),
         !(var2 %in% c("country", "country_name")))

m = map2_df(var_pairs$var1, var_pairs$var2, get_cor, country_with_predics_tidy)

corrs <- m %>%
  filter(var1 %in% c("human_predic_sim_mean", "human_predic_sim_sd"),
         !var2 %in% c("human_predic_sim_mean", "human_predic_sim_sd")) %>%
  arrange(p.value) %>%
  data.frame()

lm(human_predic_sim_sd ~
     log_pop + 
     gini_index + 
     population_density
   , country_with_predics_tidy) %>%
  summary()


lm(human_predic_sim_sd ~
     log(racial_diversity_ethnic) +
    log_area +
     log(population_density) +
     log_pop + 
     #idv   +
     log(gini_index)
   , country_with_predics_tidy) %>%
  summary()

lm(human_predic_sim_mean~ log(racial_diversity_ethnic) +
     log(area) + log(population_density) + log_pop + idv + log(gini_index), country_with_predics_tidy) %>%
  summary()


```
