---
title: "Characterizing Cross-Person and Cross-Cultural Variability in Meanings Through Millions of Sketches"
bibliography: library.bib
csl: apa6.csl
document-params: "10pt, letterpaper"

author-information: > 

 \author{Molly Lewis \\ \url{mollyllewis@gmail.com} \\ Department of Psychology \\ Carnegie Mellon University  
         \And
         \bf{Anjali Balamurugan} \\ \url{XXX} \\ XXX \\ Carnegie Mellon University 
          \And
         \bf{Bin Zheng}\\ \url{XXX} \\ XXX \\  Carnegie Mellon University 
         \And
         \bf{Gary Lupyan} \\ \url{lupyan@wisc.edu} \\ Department of Psychology \\ University of Wisconsin-Madison}
         
abstract: >
    Include no author information in the initial submission, to facilitate
    blind review.  The abstract should be one paragraph, indented 1/8 inch on both sides,
    in 9~point font with single spacing. The heading 'Abstract'
    should be 10~point, bold, centered, with one line of space below
    it. This one-paragraph abstract section is required only for standard
    six page proceedings papers. Following the abstract should be a blank
    line, followed by the header 'Keywords' and a list of
    descriptive keywords separated by semicolons, all in 9~point font, as
    shown below.
    
keywords: >
    Add your choice of indexing terms or keywords; kindly use a semi-colon; between each term.
    
output: cogsci2016::cogsci_paper
#final-submission: \cogscifinalcopy

---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.width=3, fig.height=3, fig.crop = F, 
                      fig.pos = "tb", fig.path='figs/',
                      echo=F, warning=F, cache=F, 
                      message=F, sanitize = T)


```

```{r, libraries}
library(png)
library(grid)
library(ggplot2)
library(xtable)
```



# Introduction


# Study 1:  Measuring drawing similarity computationally

# Study 2: Cross-person meaning variability

## items: which items are more variable across people? 
word predictors of variability  (Concreteness, Frequency, Semantic category, AoA)

## countries - across items, which countries have the most variability?
country predictors of variability

# Study 3: Cross-cultural meaning variability
predictors of cross-cultural similarity (Geographical distance, Cultural distance  (dspace), weather, Language distance, semantic alignment?)
interactions with item?

# Study 4: Language as a predictor of similarity


# Acknowledgements

Place acknowledgments (including funding information) in a section at
the end of the paper.

# References 

```{r}
# References will be generated automatically by Pandoc and included here.
# The following code is some latex to format the bibliography. Do not remove it.
```

\setlength{\parindent}{-0.1in} 
\setlength{\leftskip}{0.125in}
\noindent
