---
title: Conceptviz 1 analyses
author: Molly Lewis 
date: "`r Sys.Date()`"
output: 
  html_document:
    toc_float: true
    code_folding: hide
---
  
******
******
  
```{r setup, include = F}
rm(list = ls())

# load packages
library(knitr)
library(rmarkdown)
library(langcog)
library(tidyverse)
library(purrr)
library(feather)
library(forcats)
library(googlesheets)
library(jsonlite)
library(broom)
library(corrr)
#source("../R_scripts/helpers.R")

opts_chunk$set(echo = T, message = F, warning = F, 
               error = F, tidy = F, cache = T, fig.height = 4)
```

## Read in data from google sheet
```{r}
d_raw <- gs_title("conceptviz_1_data") %>%
            gs_read()

d <- map_df(d_raw$data, fromJSON, simplifyDataFrame = TRUE) %>%
  bind_cols(subj_id = d_raw$subj_id) %>%
  select(subj_id, everything()) 
```

## Tidy data
```{r}
d_tidy <- d %>%
  gather(variable, value, -subj_id) %>%
  separate(variable, c("variable", "trial_num"), sep = "_T") %>%
  spread(variable, value) %>%
  mutate_at(c("trial_num", "haus_sim", "rating", "RT", "trial_ID",  "haus_bin"), as.numeric) %>%
  mutate_at(c("category", "drawing_key_id_1", "drawing_key_id_2","trial_type", "subj_id"), as.factor)
```

## Attention Checks
```{r}
d_tidy %>%
  filter(trial_type == "attention_check") %>%
  select(subj_id, rating) %>%
  count(rating) %>%
  ggplot(aes(x = rating, y = n/200)) +
  geom_bar(stat = "identity") +
  ylab("proportion responses")+
  ggtitle("prop. attention checks") +
  theme_minimal()

mean_attention_check_ratings = d_tidy %>%
  filter(trial_type == "attention_check") %>%
  group_by(subj_id) %>% 
  summarize(mean = mean(rating)) %>%
  filter(mean < mean(.$mean))
```

Mostly 1s as correct. 

## hausdorff by decile and ratings
```{r, fig.width = 5}
d_tidy_crit <- d_tidy %>%
  filter(subj_id %in% mean_attention_check_ratings$subj_id) %>%
  filter(trial_type == "critical_trial") 

means_ratings_by_bin <- d_tidy_crit %>%
  group_by(haus_bin, category) %>%
  multi_boot_standard(column = "rating", na.rm = TRUE)

ggplot(means_ratings_by_bin, aes(x = haus_bin, y = mean, group = category, color = category)) +
  geom_pointrange(aes(ymin = summary_ci_lower, ymax = summary_ci_upper)) +
  geom_smooth(method = "lm") +
  ylab("mean similarity rating") +
  xlab("hausdorfff Distance Decile") +
  ggtitle("Similarity Ratings by hausdorff Decile") +
  scale_x_continuous(breaks = 1:10) +
  theme_minimal()
```

## hausdorff continuous and ratings
```{r, fig.width = 5}
d_tidy_crit %>%
  ggplot(aes(x = haus_sim, y = rating, group = category, color = category)) +
  geom_smooth(method = "lm") +
  ylab("mean similarity rating") +
  xlab("hausdorfff Distance") +
  ggtitle("Similarity Ratings by hausdorff Distance") +
  theme_minimal()

d_tidy_crit %>%
  group_by(category) %>%
  do(tidy(cor.test(.$rating, .$haus_sim))) %>%
  select(-parameter, -method, -alternative) %>%
  kable()
```


There's more variability in hausdorfff distance for bread, relative to tree, which explains the different slopes in the decile plot.

## Hausdorff distance, Modified Hausdorff Distance, and Imagenet-NN cosine
```{r, fig.width = 9}
tree_all_measures <- read_csv(paste0("../../../data/hausdorff_similarities/pair_sim_drawings/pair_lists/balanced_lists/tree_all_measures.csv")) %>%
    mutate_at(c("key_id_1", "key_id_2", "country_code_1","country_code_2"), as.factor) %>%
  select(key_id_1, key_id_2, hd_sim, mhd_sim, cosine, country_code_1, country_code_2) %>%
  mutate(category = "tree")

bread_all_measures <- read_csv(paste0("../../../data/hausdorff_similarities/pair_sim_drawings/pair_lists/balanced_lists/bread_all_measures.csv")) %>%
    mutate_at(c("key_id_1", "key_id_2", "country_code_1","country_code_2"), as.factor)  %>%
  select(key_id_1, key_id_2, hd_sim, mhd_sim, cosine,  country_code_1, country_code_2)  %>%
  mutate(category = "bread")

all_measures <- d_tidy_crit %>%
  rename(key_id_1 = drawing_key_id_1,
         key_id_2 = drawing_key_id_2) %>%
  left_join(bind_rows(tree_all_measures, bread_all_measures), by = c("key_id_1", "key_id_2", "category")) %>%
  select(subj_id, trial_ID, category, rating, haus_sim, mhd_sim, cosine, country_code_1, country_code_2, trial_num) %>%
  rename(hd_sim = haus_sim)

all_measures %>%
  gather("measure", "value", 3:5) %>%
  ggplot(aes(x = value, y = rating, group = category, color = category)) +
  geom_smooth(method = "lm") +
  facet_grid(. ~ measure, scales = "free") +
  theme_minimal()

all_measures %>%
  gather("measure", "value", 3:5) %>%
  group_by(category, measure) %>%
  do(tidy(cor.test(.$rating, .$value))) %>%
  select(-parameter, -method, -alternative) %>%
  kable()
```

Hausdorff Distance is better than Modified hausdorff Distance (MHD). For bread, MHD > cosine; For tree; MHD = cosine (but there's less variability).

The correlations on the continous measures are modest, but I suspect that's because there's a ceiling on the correlation because we're using a likert scale.

Measure models
```{r}
summary(lmer(rating ~ hd_sim + (1|subj_id), all_measures))

summary(lmer(rating ~ scale(hd_sim) + scale(cosine) + (trial_num|subj_id), all_measures))
summary(lm(rating ~ scale(hd_sim) + scale(cosine) , all_measures))

```

# Predicting distances from country dyadic measures measures
```{r}
precip_vars <- read_csv( "../../../data/supplementary_data/cultural_sim_measures/geo/country_climate_ratios.csv") 

all_precips <- precip_vars %>%
  bind_rows(precip_vars %>% rename(country_code_1 = country_code_2, country_code_2 = country_code_1))

all_dyadic_vars <- read_csv("../../../data/supplementary_data/cultural_sim_measures/all_dyadic_vars.csv")  %>%
  left_join(all_precips)
```

Get missing vars
```{r}
## centroids
centroids <- read_tsv("../../../data/supplementary_data/cultural_sim_measures/geo/country_centroids/country_centroids_primary.csv") %>%
  select(ISO3136, LAT, LONG) %>%
  rename(country_code = ISO3136) 

centroids_HK_GE <- centroids %>%
  filter(country_code == "GE") %>%
  bind_rows(data.frame(country_code ="HK", LAT = 22.28552, LONG = 114.15769)) %>%
  bind_rows(centroids)
  
g_centroids <- geosphere::distm(cbind(centroids_HK_GE$LONG, centroids_HK_GE$LAT)) # in meters 
rownames(g_centroids) <- centroids_HK_GE$country_code
colnames(g_centroids) <- centroids_HK_GE$country_code

all_centroid_dists <- reshape2::melt(g_centroids) %>%
  rename(country_code_1 = Var1,
         country_code_2 = Var2,
         centroid_dist_meters = value) 

#temp_precip
climate <- read_csv("../../../data/supplementary_data/cultural_sim_measures/geo/all_climiate_data.csv")

all_measures_climate <- all_measures %>%
  distinct(country_code_1, country_code_2) %>%
  left_join(climate, by = c("country_code_1" = "country_code")) %>%
  rename(temp_1 = temp,
         precip_1 = precip) %>%
  left_join(climate, by = c("country_code_2" = "country_code")) %>%
  rename(temp_2 = temp,
         precip_2 = precip) %>%
  mutate(precip_difference = abs(precip_2 - precip_1),
         temp_difference = abs(temp_2 - temp_1)) %>%
  select(country_code_1, country_code_2, precip_difference, temp_difference) 

event_dists <- read_csv("../../data/supplementary_data/cultural_sim_measures/events/all_google_event_dists.csv")

all_measures_with_dyadic <- all_measures %>%
  left_join(all_dyadic_vars) %>%
  select(-centroid_dist_meters, 
         -precip_difference, -temp_difference, -log_normalized_n_events_all, -log_normalized_mean_imports_dollars) %>%
  left_join(all_centroid_dists) %>%
  left_join(all_measures_climate) %>%
  left_join(event_dists)
```


```{r}
########### Here's are the random model: ##################################
summary(lmer(rating ~  scale(centroid_dist_meters) + (1 |category) + (1|subj_id), all_measures_with_dyadic))

summary(lmer(rating ~ scale(centroid_dist_meters) + 
               scale(log_normalized_n_events_all) + 
               (1|category) + (1|subj_id), 
              all_measures_with_dyadic))

summary(lmer(rating ~  scale(centroid_dist_meters) + category + (1 |subj_id), all_measures_with_dyadic))

summary(lmer(rating ~ scale(centroid_dist_meters) + 
               scale(log_normalized_n_events_all) + 
               category + (1 |subj_id), 
              all_measures_with_dyadic))
#####################################################################
########### Here's are the fixed model: ##################################
summary(lmer(rating ~  scale(centroid_dist_meters) * category + (1|subj_id), all_measures_with_dyadic))

summary(lmer(rating ~ scale(centroid_dist_meters) + 
               scale(log_normalized_n_events_all) + 
               (1|category) + (1|subj_id), 
              all_measures_with_dyadic))

summary(lmer(rating ~  scale(centroid_dist_meters) + category + (1 |subj_id), all_measures_with_dyadic))

summary(lmer(rating ~ scale(centroid_dist_meters) + 
               scale(log_normalized_n_events_all) + 
               category + (1 |subj_id), 
              all_measures_with_dyadic))
#####################################################################


```


```{r}




corrs <- correlate(all_measures_with_dyadic %>% select(c(-1:-3,-8:-10, -13:-16)), 
                   use = "complete.obs")  %>%
  shave()

rplot(corrs)

all_measures_with_dyadic %>%
    select(c( -9:-11, -14:-17)) %>%
    gather("dyadic_measure", "value", 9:15) %>%
    group_by(category, dyadic_measure) %>%
    do(tidy(cor.test(.$rating, .$value))) %>%
    select(-parameter, -method, -alternative) %>%
    kable()

summary(lm(rating ~ scale(log_normalized_n_events_all)  , all_measures_with_dyadic))

summary(lm(rating ~ scale(centroid_dist_meters) + 
             scale(precip_difference) + 
             scale(temp_difference)  + 
             category, all_measures_with_dyadic))



summary(lmer(rating ~ scale(centroid_dist_meters) + scale(log_normalized_n_events_all) + scale(wals_euclidean_dist) + (1 |category), all_measures_with_dyadic))

summary(lmer(rating ~ scale(log_normalized_n_events_all) + scale(centroid_dist_meters) + (1 |category) + (1 |subj_id), all_measures_with_dyadic))

summary(lm(rating ~ scale(log_normalized_n_events_all)  scale(centroid_dist_meters)  *category , all_measures_with_dyadic))

# plot each of tree and bread as a function of events, distance, and asjp


item_means <- all_measures_with_dyadic %>%
  mutate(trialname = paste0(category, trial_ID)) %>%
  group_by(trialname) %>%
  summarize(rating = mean(rating)) %>%
  left_join(all_measures_with_dyadic %>% mutate(trialname = paste0(category, trial_ID)) %>% select(-rating), by = "trialname") %>%
  group_by(trialname) %>%
  slice(1) %>%
  select(-subj_id)

item_means %>%
  filter(asjp_dist != 0) %>%
  gather("measure", "value", c(11:12,17:21)) %>%
  ggplot( aes(x = value, y = rating, color = category)) +
    geom_point() +
    geom_smooth(method = "lm") +
    facet_wrap(~measure, scales = "free")



```

# RTS
```{r}
all_measures2 <- d_tidy_crit %>%
  rename(key_id_1 = drawing_key_id_1,
         key_id_2 = drawing_key_id_2) %>%
  left_join(bind_rows(tree_all_measures, bread_all_measures), 
            by = c("key_id_1", "key_id_2", "category")) %>%
  select(category, RT, rating, haus_sim, mhd_sim, cosine) %>%
  rename(hd_sim = haus_sim)
a
all_measures2 %>%
  gather("measure", "value", 4:6) %>%
  ggplot(aes(x = value, y = log(RT), group = category, color = category)) +
  geom_smooth() +
  facet_grid(. ~ measure, scales = "free") +
  theme_minimal()

all_measures2 %>%
  gather("measure", "value", 4:6) %>%
  ggplot(aes(x = value, y = log(RT), group = category, color = category)) +
  geom_smooth() +
  facet_grid(. ~ measure, scales = "free") +
  theme_minimal()
```
